Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-25 writing/DraftExposurePaper/DraftExposurePaper.Rmd
Fix example for Ike county weather

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain1 <- right_join(ike_nldas, ike_gauge, by = "fips")
#ike_nldas <- as.data.table(alex_nldas)
#ike_gauge <- as.data.table(alex_gauge)
#compare_rain1 <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain1, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

@@

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)
#ike_weather <- weather_fips(fips = ike_fips,
                             #date_min = "2008-09-01",
                             #date_max = "2010-09-14",
                             #var = "PRCP") # Same thing here
```

>>>>

```{r echo = FALSE, fig.height = 4, fig.width = 6}
library(weathermetrics)
#library(data.table)
#ike_gauge <- read.csv("/Users/joshuaferreri/Documents/ike_rain.csv", header = TRUE)
#save(ike_gauge, file = "writing/DraftExposurePaper/ike_gauge.RData")
#load("~/Documents/hurricaneexposure/writing/DraftExposurePaper/ike_gauge.RData")
load("ike_gauge.RData")
ike_gauge$rain_mm <- convert_precip(ike_gauge$rain_in, 
                                    "inches", "mm")
ike_nldas <- county_rain(counties = unique(ike_gauge$fips),
                             start_year = 2008, end_year = 2008,
                             rain_limit = 0, dist_limit = 1500,
                             days_included = c(-2, -1, 0, 1))
ike_nldas <- ike_nldas %>%
        filter(storm_id == "Ike-2008")
ike_gauge$fips <- as.character(ike_gauge$fips)
compare_rain1 <- right_join(ike_nldas, ike_gauge, by = "fips")
#ike_nldas <- as.data.table(alex_nldas)
#ike_gauge <- as.data.table(alex_gauge)
#compare_rain1 <- left_join(alex_nldas, alex_gauge, by = "fips")
b <- ggplot(compare_rain1, aes(x = tot_precip, y = rain_mm,
                              color = fips)) +
        geom_point() + 
        theme_bw()
b
```

@@

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
#Alex-2010
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
#alex_weather <- weather_fips(fips = alex_fips,
                             #date_min = "2010-06-25",
                             #date_max = "2010-07-02",
                             #var = "PRCP") # Returns warning: "sorry, no data found"
                                            # and problemin station_ids$meta . . .
#Ike-2008
ike_fips <- ike_nldas$fips
ike_fips <- unique(ike_fips)

ike_weather <- weather_fips(fips = ike_fips[1],
                             date_min = "2008-09-01",
                             date_max = "2010-09-14",
                             var = "PRCP") # Same thing here
```
